Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-28 Grassmannian_cells.tex
Theorem 4.20 cleanup

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{
           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
      These satisfy the following relations:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
          \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

\begin{theorem}
  \label{cellscover}
  For each $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
  These cell decompositions are compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
  \begin{itemize}
    \item[($\dagger$)] for any $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, we have $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E')\neq 0$ for all $\tilde E'\in C_{\tilde E}$, where $C_{\tilde E}$ is the affine cell which contains $\tilde E$.
  \end{itemize}
% Moreover, the cell decompositions are independent of the choices made during their inductive construction.
\end{theorem}
We record the following immediate consequence before giving the proof.
\begin{corollary}
  Every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
\end{corollary}
\begin{proof}
  For the standard lifts $\tilde P_m$, this is just the special case $J=\varnothing$ in Theorem~\ref{cellscover}.
  The claim for any translate $\tilde P_{m,w}$ for $w\in W_n$ is an immediate consequence of this.
\qed\end{proof}
\subsubsection*{Proof of Theorem~\ref{cellscover}}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.

  For $m\ge2$, we work by reverse induction on $|J|$ with the base case $|J|=n-1$, say $J^c=\{j\}$.
  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ by Lemma~\ref{le:truncated quotients}.1 and thus the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$ and $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}$, where $\ui'_1=(i_2,\ldots,i_k)$, coincide for any admissible sequence $\ui\in A_1^{(k)}$, $k<m$, with $i_1=j$ and any subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$.
  By the induction on $m$, the quiver Grassmannian $\Gr_\tbfe(\tilde P_m^{\{j\}})$ admits a cell decomposition so that the compatibility condition~($\dagger$) holds for each of the maps $\tilde\pi_m^{\ui'_1,I,\{j\}}:\tilde P_m^{\{j\}}\to\tilde P_{m+1-k,\ui'_1}^I$.
  But~$\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ is naturally isomorphic to $\Gr_\tbfe(\tilde P_m^{\{j\}})$ using the action of $W_n$, under this correspondence the cell decomposition becomes compatible with the projection maps $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}:\tilde P_{m,j}^{\{j\}}\to\tilde P_{m+1-k,\ui}^I$.
  Then using the equivalence $\Gr_\tbfe(\tilde P_{m+1}^J)\cong\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ coming from Lemma~\ref{le:truncated quotients}.1, we obtain the desired cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$ which is compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$.

  Now consider $J\subsetneq I\subsetneq \{1,\ldots,n\}$ with $I\setminus J=\{j\}$.
  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi$ and $\Phi$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
  By way of induction, we assume all quiver Grassmannians $\Gr_\tbff(\tilde P_{m,j})$ and $\Gr_\tbfg(\tilde P_{m+1}^I)$ admit cell decompositions satisfying ($\dagger$), say
  \begin{equation}
    \label{eq:cellB}
    \Gr_\tbff(\tilde P_{m,j})=\coprod_{k=1}^r B_{\tbff,k}
  \end{equation}
  and
  \[\Gr_\tbfg(\tilde P_{m+1}^I)=\coprod_{\ell=1}^s C_{\tbfg,\ell}.\]
  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(\tilde F,\tilde G)\in B_{\tbff,k}\times C_{\tbfg,\ell}$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
  \begin{itemize}
    \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
    \item $m\ge3$ with $\tilde\pi_{m,j}^{j,I,\varnothing}(\tilde F)=0$.
  \end{itemize}
  By the compatibility with $\tilde\pi_{m,j}^{j,I,\varnothing}$ for the cell decomposition \eqref{eq:cellB}, we see that either all or none of the fibers over $B_{\tbff,k}\times C_{\tbfg,\ell}$ are empty.
  It follows that there is an induced cell decomposition on the image of $\Psi_{\tbff,\tbfg}$ given by those products of cells $B_{\tbff,k}\times C_{\tbfg,\ell}$ over which the fiber is not empty.
  Theorem \ref{vb} then provides a cell decomposition for $\cG_{\tbff,\tbfg}$, where cells take the form $\AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
  By Lemma~\ref{le:good partition}, we may order the affine cells in the $\cG_{\tbff,\tbfg}$ appropriately to obtain a cell decomposition of $\Gr_{\tbfe}(\tilde P_{m+1}^J)$ (c.f. Remark~\ref{rem:cell decompositions}).

  Now consider $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, say $\tilde E\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$, and assume $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and some subset $I'\subsetneq\{1,\ldots,n\}$ with $i_k\in I'$.
  There are two cases to consider:
  \begin{itemize}
    \item If $i_1\ne j$, the map $\tilde\pi_{m+1}^{\ui,I',J}$ factors as $\tilde\pi_{m+1}^{\ui,I',I}\circ\tilde\pi_{m+1}^{I,J}$ by Lemma~\ref{le:truncated quotients}.4.
      By construction, we have $\tilde\pi_{m+1}^{I,J}(\tilde E')\in C_{\tbfg,\ell}$ for all~$\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
      But $\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E)\big)=\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\ne0$ implies $\tilde\pi_{m+1}^{\ui,I',I}(\tilde G)\ne0$ for all~$\tilde G\in C_{\tbfg,\ell}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E')=\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E')\big)\neq 0$ for all $\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
    \item If $i_1=j$, the restricted map $\tilde\pi_{m+1}^{\ui,I',J}\Big|_{\tilde P_{m,j}}$ coincides with $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}$ by Lemma~\ref{le:truncated quotients}.4.
      By construction, we have $\tilde E'\cap \tilde P_{m,j}\in B_{\tbff,k}$ for all ~$\tilde E'\in \AA^d\times B_{\tbff,k} \times C_{\tbfg,\ell}$.
      But $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde E\cap\tilde P_{m,j})=\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\ne0$ implies $\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde F)\ne0$ for all~$\tilde F\in B_{\tbff,k}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E')=\tilde\pi_{m,j}^{\ui'_1,I',\varnothing}(\tilde E'\cap \tilde P_{m,j})\neq 0$ for all $\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
  \end{itemize}
  Thus the compatibility condition ($\dagger$) holds for the cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$.

>>>>

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{
           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
      These satisfy the following relations:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
        \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
        %\item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

\begin{theorem}
  \label{cellscover}
  For each $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
  These cell decompositions can be chosen compatible with the projection maps $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to\tilde P_{m+1-k,\ui}^I$ from Lemma~\ref{le:truncated quotients} in the following sense:
  \begin{itemize}
    \item[($\dagger$)] for any $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ such that $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\neq 0$ for some admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, there exists a cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$ so that $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E')\neq 0$ for all $\tilde E'\in C_{\tilde E}$, where $C_{\tilde E}$ is the affine cell which contains $\tilde E$.
  \end{itemize}
\end{theorem}
We record the following immediate consequence before giving the proof.
\begin{corollary}
  Every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
\end{corollary}
\begin{proof}
  For the standard lifts $\tilde P_m$, this is just the special case $J=\varnothing$ in Theorem~\ref{cellscover}.
  The claim for any translate $\tilde P_{m,w}$ for $w\in W_n$ is an immediate consequence of this.
\qed\end{proof}
\subsubsection*{Proof of Theorem~\ref{cellscover}}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.

  For $m\ge2$, we work by reverse induction on $|J|$ with the base case $|J|=n-1$, say $J^c=\{j\}$.
  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ by Lemma~\ref{le:truncated quotients}.1 and thus the projection maps $\tilde\pi_{m+1}^{\ui,I,J}$ and $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}$, where $\ui'_1=(i_2,\ldots,i_k)$, coincide for any admissible sequence $\ui\in A_1^{(k)}$, $k<m$, with $i_1=j$ and any subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$.
  By the induction on $m$, the quiver Grassmannian $\Gr_\tbfe(\tilde P_m^{\{j\}})$ admits a cell decomposition so that the compatibility condition~($\dagger$) holds for the map $\tilde\pi_m^{\ui'_1,I,\{j\}}:\tilde P_m^{\{j\}}\to\tilde P_{m+1-k,\ui'_1}^I$.
  But~$\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ is naturally isomorphic to $\Gr_\tbfe(\tilde P_m^{\{j\}})$ using the action of $W_n$, under this correspondence the cell decomposition becomes compatible with the projection map $\tilde\pi_{m,j}^{\ui'_1,I,\{j\}}:\tilde P_{m,j}^{\{j\}}\to\tilde P_{m+1-k,\ui}^I$.
  Then using the equivalence $\Gr_\tbfe(\tilde P_{m+1}^J)\cong\Gr_\tbfe(\tilde P_{m,j}^{\{j\}})$ coming from Lemma~\ref{le:truncated quotients}.1, we obtain the desired cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$ which is compatible with the projection map $\tilde\pi_{m+1}^{\ui,I,J}$.

  Now suppose $|J|\le n-2$ and consider an admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, with $i_1\notin J$ and a subset $I'\subsetneq\{1,\ldots,n\}$ with $i_k\in I'$.
  Taking $j\notin J$ with $j\ne i_1$, we write $I=J\cup\{j\}$.
  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi$ and $\Phi$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
  By way of induction, we assume all quiver Grassmannians $\Gr_\tbff(\tilde P_{m,j})$ and $\Gr_\tbfg(\tilde P_{m+1}^I)$ admit cell decompositions satisfying ($\dagger$) for the maps $\tilde\pi_{m,j}^{j,I',\varnothing}$ and $\tilde\pi_{m+1}^{\ui,I',I}$ respectively, say
  \begin{equation}
    \label{eq:cellB}
    \Gr_\tbff(\tilde P_{m,j})=\coprod_{k=1}^r B_{\tbff,k}
  \end{equation}
  and
  \[\Gr_\tbfg(\tilde P_{m+1}^I)=\coprod_{\ell=1}^s C_{\tbfg,\ell}.\]
  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(\tilde F,\tilde G)\in B_{\tbff,k}\times C_{\tbfg,\ell}$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied:
  \begin{itemize}
    \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
    \item $m\ge3$ with $\tilde\pi_{m,j}^{j,I,\varnothing}(\tilde F)=0$.
  \end{itemize}
  By the compatibility with $\tilde\pi_{m,j}^{j,I,\varnothing}$ for the cell decomposition \eqref{eq:cellB}, we see that either all or none of the fibers over $B_{\tbff,k}\times C_{\tbfg,\ell}$ are empty.
  It follows that there is an induced cell decomposition on the image of $\Psi_{\tbff,\tbfg}$ given by those products of cells $B_{\tbff,k}\times C_{\tbfg,\ell}$ over which the fiber is not empty.
  Theorem \ref{vb} then provides a cell decomposition for $\cG_{\tbff,\tbfg}$, where cells take the form $\AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
  By Lemma~\ref{le:good partition}, we may order the affine cells in the $\cG_{\tbff,\tbfg}$ appropriately to obtain a cell decomposition of $\Gr_{\tbfe}(\tilde P_{m+1}^J)$ (c.f. Remark~\ref{rem:cell decompositions}).

  Now consider $\tilde E\in\Gr_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, say $\tilde E\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$, and assume $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\neq 0$.
  Since $i_1\ne j$, the map $\tilde\pi_{m+1}^{\ui,I',J}$ factors as $\tilde\pi_{m+1}^{\ui,I',I}\circ\tilde\pi_{m+1}^{I,J}$ by Lemma~\ref{le:truncated quotients}.4.
  By construction, we have $\tilde\pi_{m+1}^{I,J}(\tilde E')\in C_{\tbfg,\ell}$ for all~$\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
  But $\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E)\big)=\tilde\pi_{m+1}^{\ui,I',J}(\tilde E)\ne0$ implies $\tilde\pi_{m+1}^{\ui,I',I}(\tilde G)\ne0$ for all~$\tilde G\in C_{\tbfg,\ell}$, in particular $\tilde\pi_{m+1}^{\ui,I',J}(\tilde E')=\tilde\pi_{m+1}^{\ui,I',I}\big(\tilde\pi_{m+1}^{I,J}(\tilde E')\big)\neq 0$ for all $\tilde E'\in \AA^d \times B_{\tbff,k} \times C_{\tbfg,\ell}$.
  Thus the compatibility condition ($\dagger$) with $\tilde\pi_{m+1}^{\ui,I',J}$ holds for this cell decomposition of $\Gr_\tbfe(\tilde P_{m+1}^J)$.
